---
title: "R_Probtrack_Data"
author: "Leigh Gayle Goetschius"
date: "06/27/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup}

#knitr::opts_knit$set(root.dir = normalizePath('/Users/leighgayle/Box Sync/ProbtrackX_Project/'))

```


```{r setup and load packages, include=FALSE}
library(foreign); # For reading in the data.
library(car); # For checking regression diagnostics
library(gvlma); # Global test of assumptions.
library(ggplot2);
library(moments);
library(MASS)
```

# No Scalp Data

```{r import no scalp data}

ns_data = read.csv('/Users/leighgayle/Box Sync/ProbtrackX_Project/ProbtrackData_NoScalpSubList_wDTI_2.csv', sep = ',', header = TRUE)

ns_data = read.csv('/Users/leighgayle/Box Sync/ProbtrackX_Project/ProbtrackData_NoScalpSubList_wDTI_10302018.csv', sep = ',', header = TRUE)
```

# Run some diagnostics on the no scalp data.

```{r regression diagnostics no scalp}

# Model to check multicollinearity on.
fit_R = lm(Threat_Act_Ramy_NoScalp ~ RAmySeed_BA25Target + RAmySeed_BA24Target + RAmySeed_BA47Target + RAmySeed_BA11Target + RAmySeed_BA32Target + RAmySeed_BA10Target + RAmySeed_BA9Target, data=ns_data)

fit_L = lm(Threat_Act_Lamy_NoScalp ~ LAmySeed_BA25Target + LAmySeed_BA24Target + LAmySeed_BA47Target + LAmySeed_BA11Target + LAmySeed_BA32Target + LAmySeed_BA10Target + LAmySeed_BA9Target, data=ns_data)

# Check for multi-collinearity.
vif(fit_R)
sqrt(vif(fit_R)) > 2 # If this statement is true, it's a problem. 

vif(fit_L)
sqrt(vif(fit_L)) > 2 # If this statement is true, it's a problem. 

# Perform a global validation of linear model assumptions as well as separate evaluations of skewness, kurtosis, and heteroscedasticity.
gvmodel = gvlma(fit_R)
summary(gvmodel)

gvmodel2 = gvlma(fit_L)
summary(gvmodel2)

# Fun fact, we don't have to worry about kurtosis violation for the regression models. 

# Individual kurtosis values are a different story for our t-test analysis. 
kurtosis(ns_data$RAmySeed_BA25Target)
kurtosis(ns_data$RAmySeed_BA24Target) # Large kurtosis value
kurtosis(ns_data$RAmySeed_BA47Target)
kurtosis(ns_data$RAmySeed_BA11Target)
kurtosis(ns_data$RAmySeed_BA32Target) # Large kurtosis value
kurtosis(ns_data$RAmySeed_BA10Target)
kurtosis(ns_data$RAmySeed_BA9Target) # Semi-large kurtosis value

kurtosis(ns_data$LAmySeed_BA25Target)
kurtosis(ns_data$LAmySeed_BA24Target) # Large kurtosis value
kurtosis(ns_data$LAmySeed_BA47Target)
kurtosis(ns_data$LAmySeed_BA11Target)
kurtosis(ns_data$LAmySeed_BA32Target) # Large kurtosis value
kurtosis(ns_data$LAmySeed_BA10Target)
kurtosis(ns_data$LAmySeed_BA9Target) # Semi-large kurtosis value

skewness(ns_data$LAmySeed_BA25Target)
skewness(ns_data$LAmySeed_BA24Target) 
skewness(ns_data$LAmySeed_BA47Target)
skewness(ns_data$LAmySeed_BA11Target)
skewness(ns_data$LAmySeed_BA32Target) 
skewness(ns_data$LAmySeed_BA10Target)
skewness(ns_data$LAmySeed_BA9Target)


# Check for non-independence of errors.
durbinWatsonTest(fit_R)
durbinWatsonTest(fit_L)

# Check for influential observations.
avPlots(fit_R)
avPlots(fit_L)

# Cook's D --> identify D values > 4/(n-k-1)
cutoff = 4/((nrow(ns_data) - length(fit_R$coefficients)-1))
plot(fit_R, which=4, cook.levels=cutoff)
plot(fit_L, which=4, cook.levels=cutoff)

```

# Now let's remove those outliers. 
```{r remove no scalp outliers}

#clean.ns_data = ns_data[-c(12,75,82,89,99,146), ]
clean.ns_data = ns_data[-c(12,75,82,89,99,145), ]

```

# Mean/SD of the different probability of connectivity.
```{r no scalp descriptives}

# Mean 
means = sapply(clean.ns_data, mean, na.rm = TRUE)

means

# SD
sd = sapply(clean.ns_data, sd, na.rm = TRUE)

sd

```

```{r are the connections different from zero}

# Right hemisphere
t.test(clean.ns_data$RAmySeed_BA9Target)
t.test(clean.ns_data$RAmySeed_BA10Target)
t.test(clean.ns_data$RAmySeed_BA11Target)
t.test(clean.ns_data$RAmySeed_BA24Target)
t.test(clean.ns_data$RAmySeed_BA25Target)
t.test(clean.ns_data$RAmySeed_BA32Target)
t.test(clean.ns_data$RAmySeed_BA46Target)
t.test(clean.ns_data$RAmySeed_BA47Target)

# Left hemisphere
t.test(clean.ns_data$LAmySeed_BA9Target)
t.test(clean.ns_data$LAmySeed_BA10Target)
t.test(clean.ns_data$LAmySeed_BA11Target)
t.test(clean.ns_data$LAmySeed_BA24Target)
t.test(clean.ns_data$LAmySeed_BA25Target)
t.test(clean.ns_data$LAmySeed_BA32Target)
t.test(clean.ns_data$LAmySeed_BA46Target)
t.test(clean.ns_data$LAmySeed_BA47Target)

```


# T-tests between the different BA and the control tract (BA 23)
```{r comp_control_tract}

# Right hemisphere.
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA25Target)
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA24Target) # BA 24 may violate kurtosis assumptions
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA32Target) # BA 32 may violate kurtosis assumptions
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA10Target)
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA9Target)
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA11Target)
t.test(clean.ns_data$RAmySeed_BA46Target, clean.ns_data$RAmySeed_BA47Target)

# Left hemisphere.
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA25Target)
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA24Target) # BA 24 may violate kurtosis assumptions
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA32Target) # BA 32 may violate kurtosis assumptions
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA10Target)
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA9Target)
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA11Target)
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$LAmySeed_BA47Target)

# Comparing control tracts
t.test(clean.ns_data$LAmySeed_BA46Target, clean.ns_data$RAmySeed_BA46Target)

```

```{r test against BA 23}

# Right hemisphere.
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA25Target)
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA24Target) # BA 24 may violate kurtosis assumptions
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA32Target) # BA 32 may violate kurtosis assumptions
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA10Target)
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA9Target)
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA11Target)
t.test(clean.ns_data$RAmySeed_BA23Target, clean.ns_data$RAmySeed_BA47Target)

# Left hemisphere.
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA25Target)
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA24Target) # BA 24 may violate kurtosis assumptions
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA32Target) # BA 32 may violate kurtosis assumptions
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA10Target)
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA9Target)
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA11Target)
t.test(clean.ns_data$LAmySeed_BA23Target, clean.ns_data$LAmySeed_BA47Target)

```

```{r against each other}

# Right BA 25 versus everyone
t.test(clean.ns_data$RAmySeed_BA25Target,clean.ns_data$RAmySeed_BA10Target)
t.test(clean.ns_data$RAmySeed_BA25Target,clean.ns_data$RAmySeed_BA11Target)
t.test(clean.ns_data$RAmySeed_BA25Target,clean.ns_data$RAmySeed_BA9Target)
t.test(clean.ns_data$RAmySeed_BA25Target,clean.ns_data$RAmySeed_BA32Target)
t.test(clean.ns_data$RAmySeed_BA25Target,clean.ns_data$RAmySeed_BA24Target)
t.test(clean.ns_data$RAmySeed_BA25Target,clean.ns_data$RAmySeed_BA47Target) #ns

# Left BA 25 versus everyone
t.test(clean.ns_data$LAmySeed_BA25Target,clean.ns_data$LAmySeed_BA10Target)
t.test(clean.ns_data$LAmySeed_BA25Target,clean.ns_data$LAmySeed_BA11Target)
t.test(clean.ns_data$LAmySeed_BA25Target,clean.ns_data$LAmySeed_BA9Target)
t.test(clean.ns_data$LAmySeed_BA25Target,clean.ns_data$LAmySeed_BA32Target)
t.test(clean.ns_data$LAmySeed_BA25Target,clean.ns_data$LAmySeed_BA24Target)
t.test(clean.ns_data$LAmySeed_BA25Target,clean.ns_data$LAmySeed_BA47Target)

# Right BA 47 versus everyone
t.test(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$RAmySeed_BA10Target)
t.test(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$RAmySeed_BA11Target)
t.test(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$RAmySeed_BA9Target)
t.test(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$RAmySeed_BA32Target)
t.test(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$RAmySeed_BA24Target)
t.test(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$RAmySeed_BA25Target) #ns

# Left BA 47 versus everyone
t.test(clean.ns_data$LAmySeed_BA47Target,clean.ns_data$LAmySeed_BA10Target)
t.test(clean.ns_data$LAmySeed_BA47Target,clean.ns_data$LAmySeed_BA11Target) #ns
t.test(clean.ns_data$LAmySeed_BA47Target,clean.ns_data$LAmySeed_BA9Target)
t.test(clean.ns_data$LAmySeed_BA47Target,clean.ns_data$LAmySeed_BA32Target)
t.test(clean.ns_data$LAmySeed_BA47Target,clean.ns_data$LAmySeed_BA24Target)
t.test(clean.ns_data$LAmySeed_BA47Target,clean.ns_data$LAmySeed_BA25Target) # 25 higher than 47

# Right 24 versus everyone --> BA24 is less than all of the statisically significant t.tests
t.test(clean.ns_data$RAmySeed_BA24Target,clean.ns_data$RAmySeed_BA10Target) 
t.test(clean.ns_data$RAmySeed_BA24Target,clean.ns_data$RAmySeed_BA11Target) 
t.test(clean.ns_data$RAmySeed_BA24Target,clean.ns_data$RAmySeed_BA9Target) #ns
t.test(clean.ns_data$RAmySeed_BA24Target,clean.ns_data$RAmySeed_BA32Target) #ns
t.test(clean.ns_data$RAmySeed_BA24Target,clean.ns_data$RAmySeed_BA47Target)
t.test(clean.ns_data$RAmySeed_BA24Target,clean.ns_data$RAmySeed_BA25Target)

# Left 24 versus everyone --> except where marked, BA24 is less than the other regions.
t.test(clean.ns_data$LAmySeed_BA24Target,clean.ns_data$LAmySeed_BA10Target)
t.test(clean.ns_data$LAmySeed_BA24Target,clean.ns_data$LAmySeed_BA11Target)
t.test(clean.ns_data$LAmySeed_BA24Target,clean.ns_data$LAmySeed_BA9Target)  # 24 higher than 9 here.
t.test(clean.ns_data$LAmySeed_BA24Target,clean.ns_data$LAmySeed_BA32Target) #p=.03
t.test(clean.ns_data$LAmySeed_BA24Target,clean.ns_data$LAmySeed_BA47Target)
t.test(clean.ns_data$LAmySeed_BA24Target,clean.ns_data$LAmySeed_BA25Target)

# Right 10 versus everyone --> all tests are significant here
t.test(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$RAmySeed_BA24Target) 
t.test(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$RAmySeed_BA11Target) # 11 is stronger
t.test(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$RAmySeed_BA9Target) 
t.test(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$RAmySeed_BA32Target) 
t.test(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$RAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$RAmySeed_BA25Target) # 25 is stronger

# Left 10 versus everyone
t.test(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$LAmySeed_BA24Target)
t.test(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$LAmySeed_BA11Target) # 11 is stronger
t.test(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$LAmySeed_BA9Target)  
t.test(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$LAmySeed_BA32Target) 
t.test(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$LAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$LAmySeed_BA25Target) # 25 is stronger

# Right 11 versus everyone -
t.test(clean.ns_data$RAmySeed_BA11Target,clean.ns_data$RAmySeed_BA24Target) 
t.test(clean.ns_data$RAmySeed_BA11Target,clean.ns_data$RAmySeed_BA10Target) 
t.test(clean.ns_data$RAmySeed_BA11Target,clean.ns_data$RAmySeed_BA9Target) 
t.test(clean.ns_data$RAmySeed_BA11Target,clean.ns_data$RAmySeed_BA32Target) 
t.test(clean.ns_data$RAmySeed_BA11Target,clean.ns_data$RAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$RAmySeed_BA11Target,clean.ns_data$RAmySeed_BA25Target) # 25 is stronger

# Left 11 versus everyone
t.test(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$LAmySeed_BA24Target)
t.test(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$LAmySeed_BA10Target) 
t.test(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$LAmySeed_BA9Target)  
t.test(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$LAmySeed_BA32Target) 
t.test(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$LAmySeed_BA47Target) # ns
t.test(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$LAmySeed_BA25Target) # 25 is stronger

# Right 32 versus everyone 
t.test(clean.ns_data$RAmySeed_BA32Target,clean.ns_data$RAmySeed_BA24Target) # ns
t.test(clean.ns_data$RAmySeed_BA32Target,clean.ns_data$RAmySeed_BA10Target) # 10 is stronger
t.test(clean.ns_data$RAmySeed_BA32Target,clean.ns_data$RAmySeed_BA9Target) # ns
t.test(clean.ns_data$RAmySeed_BA32Target,clean.ns_data$RAmySeed_BA11Target) # 11 is stronger
t.test(clean.ns_data$RAmySeed_BA32Target,clean.ns_data$RAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$RAmySeed_BA32Target,clean.ns_data$RAmySeed_BA25Target) # 25 is stronger

# Left 32 versus everyone
t.test(clean.ns_data$LAmySeed_BA32Target,clean.ns_data$LAmySeed_BA24Target) # p=.03 with 24 stronger
t.test(clean.ns_data$LAmySeed_BA32Target,clean.ns_data$LAmySeed_BA10Target) # 10 is stronger
t.test(clean.ns_data$LAmySeed_BA32Target,clean.ns_data$LAmySeed_BA9Target)  #ns
t.test(clean.ns_data$LAmySeed_BA32Target,clean.ns_data$LAmySeed_BA11Target) # 11 is stronger
t.test(clean.ns_data$LAmySeed_BA32Target,clean.ns_data$LAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$LAmySeed_BA32Target,clean.ns_data$LAmySeed_BA25Target) # 25 is stronger

# Right 9 versus everyone 
t.test(clean.ns_data$RAmySeed_BA9Target,clean.ns_data$RAmySeed_BA24Target) # ns
t.test(clean.ns_data$RAmySeed_BA9Target,clean.ns_data$RAmySeed_BA10Target) # 10 is stronger
t.test(clean.ns_data$RAmySeed_BA9Target,clean.ns_data$RAmySeed_BA11Target) # 11 is stronger
t.test(clean.ns_data$RAmySeed_BA9Target,clean.ns_data$RAmySeed_BA32Target) # ns
t.test(clean.ns_data$RAmySeed_BA9Target,clean.ns_data$RAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$RAmySeed_BA9Target,clean.ns_data$RAmySeed_BA25Target) # 25 is stronger

# Left 9 versus everyone 
t.test(clean.ns_data$LAmySeed_BA9Target,clean.ns_data$LAmySeed_BA24Target) # 24 is stronger
t.test(clean.ns_data$LAmySeed_BA9Target,clean.ns_data$LAmySeed_BA10Target) # 10 is stronger
t.test(clean.ns_data$LAmySeed_BA9Target,clean.ns_data$LAmySeed_BA11Target) # 11 is stronger  
t.test(clean.ns_data$LAmySeed_BA9Target,clean.ns_data$LAmySeed_BA32Target) # ns
t.test(clean.ns_data$LAmySeed_BA9Target,clean.ns_data$LAmySeed_BA47Target) # 47 is stronger
t.test(clean.ns_data$LAmySeed_BA9Target,clean.ns_data$LAmySeed_BA25Target) # 25 is stronger

```

```{r some other fun tests}

range(clean.ns_data$RAmySeed_BA24Target)
range(clean.ns_data$RAmySeed_BA32Target)
range(clean.ns_data$RAmySeed_BA25Target)
range(clean.ns_data$RAmySeed_BA47Target)
range(clean.ns_data$RAmySeed_BA9Target)
range(clean.ns_data$RAmySeed_BA10Target)
range(clean.ns_data$RAmySeed_BA11Target)

range(clean.ns_data$RAmySeed_BA46Target) # control tract

range(clean.ns_data$LAmySeed_BA24Target)
range(clean.ns_data$LAmySeed_BA32Target)
range(clean.ns_data$LAmySeed_BA25Target)
range(clean.ns_data$LAmySeed_BA47Target)
range(clean.ns_data$LAmySeed_BA9Target)
range(clean.ns_data$LAmySeed_BA10Target)
range(clean.ns_data$LAmySeed_BA11Target)

range(clean.ns_data$LAmySeed_BA46Target) # control tract



```

## Some fun plots.

```{r some fun plots}

#r_vals = read.csv('/Users/leighgayle/Box Sync/Final_619_Docs/predicted_r_vals_final_120117.csv', sep = ',', header = TRUE)
r_vals = read.csv('/Users/leighgayle/Box Sync/Final_619_Docs/predicted_r_vals_final_103018.csv', sep = ',', header = TRUE)

#l_vals = read.csv('/Users/leighgayle/Box Sync/Final_619_Docs/predicted_l_vals_final_120117.csv', sep = ',', header = TRUE)
l_vals = read.csv('/Users/leighgayle/Box Sync/Final_619_Docs/predicted_l_vals_final_103018.csv', sep = ',', header = TRUE)

right_cor = cor.test(r_vals$Observed,r_vals$Predicted)
right_cor

left_cor = cor.test(l_vals$observed,l_vals$Predicted)
left_cor

# Set Font family.
op <- par(family = "serif")

plot(r_vals$Observed, r_vals$Predicted, xlim = c(-1, 2.5), ylim = c(0,1.2), xlab = 'Observed R.Amy Activation', ylab = '\n Predicted R.Amy Activation', pch=16, family = 'serif',ps=4, font.lab=1, cex.lab=1.3, cex.main=2, bty = 'no')
legend(x='bottomright',legend=expression('R'^2* ' = 0.140'), bty='n', text.font=2.5, cex = 1.3)
abline(lm(r_vals$Predicted ~ r_vals$Observed))

plot(l_vals$observed, l_vals$Predicted, xlim = c(-1, 2.5), ylim = c(0,1.2), xlab = 'Observed L.Amy Activation', ylab = '\n Predicted L.Amy Activation', pch=16, family = 'serif',ps=4, font.lab=1, cex.lab=1.3, cex.main=2, bty = 'no')
legend(x='bottomright',legend=expression('R'^2* ' = .141'), bty='n', text.font=2, cex=1.3)
abline(lm(l_vals$Predicted ~ l_vals$observed))

```

```{r Plot BA47 and RAmy}

plot(clean.ns_data$RAmySeed_BA47Target,clean.ns_data$Threat_Act_Ramy_NoScalp, xlim=c(0.0,0.4), ylim=c(-1,3), xlab = 'Maximum Likelihood of Connectivity between RAmy and R BA 47', ylab = 'RAmy Activation Contrast Value', bty='no', pch=16, ps=4, font.lab=1, cex.lab=1.3, cex.main=2, family='serif')

abline(lm(clean.ns_data$Threat_Act_Ramy_NoScalp ~ clean.ns_data$RAmySeed_BA47Target))

```

```{r Plot RAmy and BA10}

plot(clean.ns_data$RAmySeed_BA10Target,clean.ns_data$Threat_Act_Ramy_NoScalp, xlim=c(0.0,0.23), ylim=c(-1,3), xlab = 'Maximum Likelihood of Connectivity between RAmy and R BA 10', ylab = 'RAmy Activation Contrast Value', bty='no', pch=16, ps=4, font.lab=1, cex.lab=1.3, cex.main=2.2, family='serif')

abline(lm(clean.ns_data$Threat_Act_Ramy_NoScalp ~ clean.ns_data$RAmySeed_BA10Target))

```


```{r Plot LAmy and BA10}

plot(clean.ns_data$LAmySeed_BA10Target,clean.ns_data$Threat_Act_Lamy_NoScalp, xlim=c(0.0,0.10), ylim=c(-.5,2.5), xlab = 'Maximum Likelihood of Connectivity between LAmy and L BA 10', ylab = 'LAmy Activation Contrast Value', bty='no', pch=16, ps=4, font.lab=1, cex.lab=1.3, cex.main=2, family='serif')

abline(lm(clean.ns_data$Threat_Act_Lamy_NoScalp ~ clean.ns_data$LAmySeed_BA10Target))

```

```{r Plot LAmy and BA11}

plot(clean.ns_data$LAmySeed_BA11Target,clean.ns_data$Threat_Act_Lamy_NoScalp, xlim=c(0.0,0.10), ylim=c(-.5,2.5), xlab = 'Maximum Likelihood of Connectivity between LAmy and L BA 11', ylab = 'LAmy Activation Contrast Value', bty='no', pch=16, ps=4, font.lab=1, cex.lab=1.3, cex.main=2, family='serif')

abline(lm(clean.ns_data$Threat_Act_Lamy_NoScalp ~ clean.ns_data$LAmySeed_BA11Target))

```

### Make plot comparing Amygdala Connectivity per hemisphere
```{r}
par(family = 'serif', font.lab=2, font.axis=2, ps=10)
boxplot(clean.ns_data$LAmySeed_BA25Target, clean.ns_data$LAmySeed_BA47Target, clean.ns_data$LAmySeed_BA11Target, clean.ns_data$LAmySeed_BA10Target, clean.ns_data$LAmySeed_BA24Target, clean.ns_data$LAmySeed_BA9Target, clean.ns_data$LAmySeed_BA32Target, names=c('BA25', 'BA47', 'BA11', 'BA10', 'BA24', 'BA9', 'BA32'), ylim=c(0,.25), ylab='Amygdala Connectivity (Max. Likelihood)', font.lab=2, cex.lab=1.6, cex.axis=1.5, family= 'serif', frame.plot=FALSE, outline=FALSE)

par(family = 'serif', font.lab=2, font.axis=2, ps=10)
boxplot(clean.ns_data$RAmySeed_BA25Target, clean.ns_data$RAmySeed_BA47Target, clean.ns_data$RAmySeed_BA11Target, clean.ns_data$RAmySeed_BA10Target, clean.ns_data$RAmySeed_BA24Target, clean.ns_data$RAmySeed_BA9Target, clean.ns_data$RAmySeed_BA32Target, names=c('BA25', 'BA47', 'BA11', 'BA10', 'BA24', 'BA9', 'BA32'), ylim=c(0,.4), ylab='Amygdala Connectivity (Max. Likelihood)', font.lab=2, cex.lab=1.6, cex.axis = 1.5, family= 'serif', frame.plot=FALSE, outline=FALSE)

```

#### I want to see if any of my tractography variables are associated with framewise displacement. I feel like that will be a motion start. 

```{r}
FDdata = read.csv('/Users/leighgayle/Box Sync/ProbtrackX_Project/FD_IncludedData.csv')
```

```{r}

# Right hemisphere
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA47Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA25Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA24Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA32Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA10Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA11Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$RAmySeed_BA9Target)

# Left hemisphere
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA47Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA25Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA24Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA32Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA10Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA11Target)
cor.test(FDdata$RelativeFramewiseDisplacement_mm, clean.ns_data$LAmySeed_BA9Target) # This is associated (wouldn't survive multiple comparisons test, but I'm not sure if you do those when you're doing a motion check)

```

# Additional analyses for the R&R in NeuroImage - begun 1.8.2019

```{r}
# import income data
income_final_4_10_18 <- read_sav("/Volumes/lsa-research02/csmonk/csmonk-lab/Data/Fragile_Families/Data Cleaning Protocol/Parent Demo/Cleaned Data/income_final_4_10_18.sav")

# create ID variable to match on. 
income_final_4_10_18$id_short = income_final_4_10_18$id
ns_data$id_short = substr(ns_data$ID, 0, 5)

Income = income_final_4_10_18[ c("id_short", "yr_income")]
clean.ns_data = merge(clean.ns_data, Income, by="id_short")

puberty = read.csv('/Users/leighgayle/Box Sync/FF_Demographics/FullSample_Puberty.csv')
puberty = puberty[ c("id_short","puberty_score","used_parent")]

clean.ns_data = merge(clean.ns_data, puberty, by="id_short")

internalizing = read.csv('/Users/leighgayle/Box Sync/ThreatDep_Probtrack_Amygdala/Internalizing_OneFactorScore_FullDataSet_092618.csv')
internalizing = internalizing[ c("id_short","Internalizing")]

clean.ns_data = merge(clean.ns_data, internalizing, by = "id_short")

amygdala_data = read.csv('/Users/leighgayle/Box Sync/Final_619_Docs/NeuroImage_Submission/R&R/extracted_amygdala_happy_sad.csv')
clean.ns_data = merge(clean.ns_data, amygdala_data, by = "id_short")

clean.ns_data = read.csv('/Users/leighgayle/Box Sync/Final_619_Docs/NeuroImage_Submission/R&R/clean_updated_datafile.csv')

MFQ = read.csv('/Users/leighgayle/Box Sync/FF_Demographics/MFQ_C_c071718.csv')
MFQ = MFQ[ c("id_short","MFQ_C_Sum")]
clean.ns_data = merge(clean.ns_data, MFQ, by = "id_short")

SCARED = read.csv('/Users/leighgayle/Box Sync/FF_Demographics/SCARED_C_c071718.csv')
SCARED = SCARED[ c("id_short","SCARED_C_Sum")]
clean.ns_data = merge(clean.ns_data, SCARED, by = "id_short")

```

```{r}

# Mark the missing values as NA
clean.ns_data$yr_income[clean.ns_data$yr_income==-99] = NA
clean.ns_data$yr_income[clean.ns_data$yr_income==88] = NA
clean.ns_data$yr_income[clean.ns_data$yr_income==77] = NA


```

#### See how income relates to the white matter metrics
```{r}

library(Hmisc);

R_vars = c("yr_income","puberty_score","Internalizing","RAmySeed_BA25Target", "RAmySeed_BA24Target","RAmySeed_BA32Target", "RAmySeed_BA47Target", "RAmySeed_BA9Target", "RAmySeed_BA10Target", "RAmySeed_BA11Target")

R_vars = c("yr_income","puberty_score","MFQ_C_Sum","SCARED_C_Sum","RAmySeed_BA25Target", "RAmySeed_BA24Target","RAmySeed_BA32Target", "RAmySeed_BA47Target", "RAmySeed_BA9Target", "RAmySeed_BA10Target", "RAmySeed_BA11Target")

R_data = clean.ns_data[R_vars]

rcorr(as.matrix(R_data))

```

```{r}
L_vars = c("yr_income", "puberty_score","Internalizing","LAmySeed_BA25Target", "LAmySeed_BA24Target","LAmySeed_BA32Target", "LAmySeed_BA47Target", "LAmySeed_BA9Target", "LAmySeed_BA10Target", "LAmySeed_BA11Target")

L_vars = c("yr_income", "puberty_score","MFQ_C_Sum","SCARED_C_Sum","LAmySeed_BA25Target", "LAmySeed_BA24Target","LAmySeed_BA32Target", "LAmySeed_BA47Target", "LAmySeed_BA9Target", "LAmySeed_BA10Target", "LAmySeed_BA11Target")

L_data = clean.ns_data[L_vars]

rcorr(as.matrix(L_data))
```

```{r}
t.test(clean.ns_data$RAmySeed_BA9Target ~ clean.ns_data$Gender) # marginal
t.test(clean.ns_data$RAmySeed_BA10Target ~ clean.ns_data$Gender)
t.test(clean.ns_data$RAmySeed_BA11Target ~ clean.ns_data$Gender)
t.test(clean.ns_data$RAmySeed_BA24Target ~ clean.ns_data$Gender)
t.test(clean.ns_data$RAmySeed_BA25Target ~ clean.ns_data$Gender) # significant
t.test(clean.ns_data$RAmySeed_BA32Target ~ clean.ns_data$Gender) # marginal
t.test(clean.ns_data$RAmySeed_BA47Target ~ clean.ns_data$Gender)
```

```{r}
t.test(clean.ns_data$LAmySeed_BA9Target ~ clean.ns_data$Gender) 
t.test(clean.ns_data$LAmySeed_BA10Target ~ clean.ns_data$Gender)
t.test(clean.ns_data$LAmySeed_BA11Target ~ clean.ns_data$Gender)
t.test(clean.ns_data$LAmySeed_BA24Target ~ clean.ns_data$Gender) # significant
t.test(clean.ns_data$LAmySeed_BA25Target ~ clean.ns_data$Gender) 
t.test(clean.ns_data$LAmySeed_BA32Target ~ clean.ns_data$Gender) 
t.test(clean.ns_data$LAmySeed_BA47Target ~ clean.ns_data$Gender)
```

```{r}
summary(lm(happyGTbaseline_left ~ LAmySeed_BA9Target + LAmySeed_BA10Target + LAmySeed_BA11Target + LAmySeed_BA24Target + LAmySeed_BA25Target + LAmySeed_BA32Target + LAmySeed_BA47Target, data = clean.ns_data))

summary(lm(sadGTbaseline_left ~ LAmySeed_BA9Target + LAmySeed_BA10Target + LAmySeed_BA11Target + LAmySeed_BA24Target + LAmySeed_BA25Target + LAmySeed_BA32Target + LAmySeed_BA47Target, data = clean.ns_data))

summary(lm(happyGTbaseline_right ~ RAmySeed_BA9Target + RAmySeed_BA10Target + RAmySeed_BA11Target + RAmySeed_BA24Target + RAmySeed_BA25Target + RAmySeed_BA32Target + RAmySeed_BA47Target, data = clean.ns_data))

summary(lm(sadGTbaseline_right ~ RAmySeed_BA9Target + RAmySeed_BA10Target + RAmySeed_BA11Target + RAmySeed_BA24Target + RAmySeed_BA25Target + RAmySeed_BA32Target + RAmySeed_BA47Target, data = clean.ns_data))

summary(lm(allfacesGTbaseline_left ~ LAmySeed_BA9Target + LAmySeed_BA10Target + LAmySeed_BA11Target + LAmySeed_BA24Target + LAmySeed_BA25Target + LAmySeed_BA32Target + LAmySeed_BA47Target, data = clean.ns_data))

summary(lm(allfacesGTbaseline_right ~ RAmySeed_BA9Target + RAmySeed_BA10Target + RAmySeed_BA11Target + RAmySeed_BA24Target + RAmySeed_BA25Target + RAmySeed_BA32Target + RAmySeed_BA47Target, data = clean.ns_data))

```

